
\begin{frame}[allowframebreaks=0.8]{Pitfalls}
  \begin{itemize}
    \item The packages Beamer-3.10 and PGF-2.10 are required. Update your \TeX{}
      installation if necessary.
    \item The template works only with pdf\LaTeX{}. Therefore, graphics files
      for inclusion should be provided in the PDF format for all kinds of
      graphics (line graphics, bitmapped images, photographs), PNG for
      artificially created bitmapped material and photographs, JPEG for
      photographs. Existing EPS files can be converted to PDF using {\tt
      epstopdf}, which should be part of every \TeX{} installation.
    \item This template uses \alert{CM-Bright} as the main text font. It looks
      good and, unlike CM-Sans which Beamer uses by default, it comes with a
      suitable math font. Make sure that CM-Bright is installed as Type-1 font
      in your \TeX{} system. For this, you need the packages `cm-super' and
      `hfbright' (use the package manager of your \TeX{} system for
      installation). Otherwise, the bitmapped version of the font is used and
      the final PDF is of bad quality.
    \item If you want Arial or Helvetica, as recommended by the corporate design
      guidelines, you can adjust this in the header of the source file of this
      document. As both fonts lack a matching math font, the template uses
      CM-Bright for the glyphs in math mode. For Arial you need the `arial' and
      for Helvetica the `helvet' \LaTeX{} packages. Package `hfbright' is needed
      for the math glyphs.
  \end{itemize}
\end{frame}

